---
title: "Titanic Notebook"
output: html_notebook
---
# Importing Imports
```{r}
#install.packages('tidyverse')
library(tidyverse)
library(dplyr)
library(ggplot2)
```
# bringing over dataset
```{r}
df <- read.csv("C:/Users/patty/OneDrive/Desktop/R_project/train (2).csv")
df
```

checking for null values in the data
```{r}
# Using tidyR
df %>% summarize(na_count = sum(is.na(df)))

# Using base R:
colSums(is.na(df))
```

#filling in those null values 

#filling in null values per column
```{r}
df$Age[is.na(df$Age)] <- mean(df$Age, na.rm= TRUE)
```

```{r}
df$RoomService[is.na(df$RoomService)] <- mean(df$RoomService, na.rm= TRUE)
```

```{r}
df$FoodCourt[is.na(df$FoodCourt)] <- mean(df$FoodCourt, na.rm= TRUE)
```

```{r}
df$ShoppingMall[is.na(df$ShoppingMall)] <- mean(df$ShoppingMall, na.rm= TRUE)
```

```{r}
df$Spa[is.na(df$Spa)] <- mean(df$Spa, na.rm= TRUE)
```

```{r}
df$VRDeck[is.na(df$VRDeck)] <- mean(df$VRDeck, na.rm= TRUE)
```

# recheking for null values / Making sure data is complete 

```{r}
# Using tidyR
df %>% summarize(na_count = sum(is.na(df)))

# Using base R:
colSums(is.na(df))
```








# creating visuals

```{r}
#age_df <- filter.data.frame(df, age=='0-10' | age=='11-19' | age=='20-29' | age=='30-39')- didnt work 
```

# finding out how many passengers are VIP
```{r}
Vip <- df$VIP
counts<-table(Vip)
```


```{r}
pie(counts, labels = names(counts))
colors <- c("black", "yellow", "orange")
pie(counts, names = names, col = colors, main = "Passengers that are vip")
```
# False means most of the passengers were not VIP

# # Finding out how many Passengers chose to sleep during their voyage 
```{r}
CryoSleep <- df$CryoSleep
counts <- table(CryoSleep)
```


```{r}
pie(counts, labels = names(counts))
colors <- c("blue", "green", "red")
pie(counts, names = names, col = colors, main = "Passengers that chose to sleep")
```

```{r}
x <- df('age')
y <- df('cryosleep')
plot(x, y, main = "Correlation between cryosleep and age", xlab = "X", ylab = "Y")
```


```{r}
qplot(log(ShoppingMall), log(Spa), data = df)
```

```{r}
# Creates the histogram
qplot(Age, data=df, binwidth=100) + 
  # Creates the titles and axis labels
  labs(x='Age', y = 'CryoSleep', title = 'CryoSleep / Age')+
  # Adjusts the title positioning
  theme(plot.title = element_text(hjust=0.5))
```
# creating a pie chart of those Passengers that chose to be transported 
```{r}
Transported <- df$Transported
counts<-table(Transported)
```

```{r}
pie(counts, labels = names(counts))
colors <- c("blue", "pink")
pie(counts, names = names, col = colors, main = "Pie chart of Passengers that chose to be Transported")
```
# It seems to be that it was a 50 / 50. Half of the passengers chose to be transported and the others didn't


